---
title: "Using `dragondown` to Write Your Thesis"
author: "Tyler Bradley"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ['xaringan-themer.css', 'using-dragondown-styles.css']
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      after_body: insert-logo.html
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
duo(
  primary_color = "#07294D", 
  secondary_color = "#FFC600",
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```

# Agenda

.xlarge[
  1. Introduction
  
2. What is Rmarkdown

3. Using `dragondown`

4. Live Demo

5. Version Control

]

---

# What is `dragondown`?

.large[

  - `dragondown` is an R package that allows you to write your thesis in Rmarkdown
  
- Provides the required templates to properly format your thesis or dissertation in the Drexel format
  
- Easily integrate text, code and outputs 
  
- Allows you to focus on your research and not think about the minute formatting details often required with other text editors (e.g. LaTeX)
  
]
 

---

# What is Rmarkdown?

.xlarge[
A framework for authoring documents allowing you to easily integrate code and text to produce high quality output!

]

Benefits:
.small[
  - Integrate code directly into your text in a variety of languages (e.g. R, python, SQL, etc.)
- Reduces copy/pasting
- Allows users to integrate version control effectively
- Easily re-render if data (or anything else) changes
]

---
class: center, inverse, middle

# Live Demo

---

# Why use `dragondown`?

.large[`dragondown` takes all of the benefits of using Rmarkdown and wraps them up with a shiny bow*]

.large[Allows you to break about your dissertation chapters to make them more manageable while still bundling them all together correctly]

.large[Provides a structured framework for effectively storing all of the materials associated with your dissertation]

.footnote[*shiny bow includes handling all formatting requirements of a Drexel dissertation]

---

## The shiny bow (i.e. formatting)



---

## Managing your chapters (i.e. index)


---

## Structured Framework (i.e. Neat Files)


---
class: center, middle, inverse

# Live Demo
