<!--
This is for including Chapter 1.  Notice that it's also good practice to name your chunk.  This will help you debug potential issues as you knit.  The chunk above is called intro and the one below is called chapter1.  Feel free to change the name of the Rmd file as you wish, but don't forget to change it here from chap1.Rmd.
-->

<!--
The {#rmd-basics} text after the chapter declaration will allow us to link throughout the document back to the beginning of Chapter 1.  These labels will automatically be generated (if not specified) by changing the spaces to hyphens and capital letters to lowercase.  Look for the reference to this label at the beginning of Chapter 2.
-->

# My First Chapter {#first-chapter}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{r load-libraries}
library(tidyverse)
library(readxl)
library(knitr)
```

## Introduction

Ipsum odio nibh tempus curabitur hendrerit urna dapibus montes magna himenaeos. Quam vivamus odio fermentum quisque imperdiet a vehicula felis dignissim. Etiam montes nulla litora magnis justo himenaeos id diam. Commodo arcu magna ligula varius. Posuere ridiculus nisi vitae fringilla ullamcorper sociosqu dignissim pellentesque cum ridiculus tempus quis eu dictum augue elementum purus mauris.

Sit cum accumsan cras nibh volutpat netus iaculis. Ultricies elementum eget mollis arcu risus habitasse dictumst mi. Potenti ultrices leo sem felis pellentesque conubia ligula orci fames. Netus proin tempor iaculis sollicitudin himenaeos netus etiam nulla varius pharetra. Lacus aptent neque ut congue molestie interdum commodo class placerat molestie cras vitae donec ultricies?

```{r read-data}
elrod_dat <- read_excel("data/Elrod_2020_2_17_Treated_Virgin.xlsx", 
                        col_names = c("sample", "value"))

kable(head(elrod_dat))
```

```{r elrod-tidy}
elrod_tidy <- elrod_dat %>% 
  mutate(
    group = str_extract(sample, "[A-C]$"),
    sample = as.numeric(str_replace(sample, "[A-C]$", ""))
  ) %>% 
  group_by(group, sample) %>% 
  summarize(
    min = min(value),
    max = max(value),
    median = median(value)
  ) 

kable(head(elrod_tidy))
```

## Including Plots

Ipsum fermentum cubilia dictumst pretium sodales pharetra porttitor odio malesuada primis nascetur. Curabitur mus pulvinar nulla egestas ullamcorper class. Mattis rutrum vestibulum orci rutrum litora suspendisse ullamcorper vulputate venenatis suscipit.

```{r elrod-plot}
elrod_tidy %>% 
  ggplot(aes(sample, median, color = group)) + 
  geom_point() +
  geom_line() + 
  geom_errorbar(aes(ymin = min, ymax = max)) + 
  theme_bw()

```


## Using python

Sit cum accumsan cras nibh volutpat netus iaculis. Ultricies elementum eget mollis arcu risus habitasse dictumst mi. Potenti ultrices leo sem felis pellentesque conubia ligula orci fames. Netus proin tempor iaculis sollicitudin himenaeos netus etiam nulla varius pharetra. Lacus aptent neque ut congue molestie interdum commodo class placerat molestie cras vitae donec ultricies?

```{using-python, eval = FALSE}
library(reticulate)
use_miniconda("/Users/tylerbradley/miniconda2/bin/python")
```

```{python, eval = FALSE}
import pandas as pd
```

